Copulas and their potential for ecology

### 2019-10-01 Paper.Rmd
error fixed in table

```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
options(scipen = 1, digits = 2) #This option round all numbers appeared in the inline r code upto specified digit
#seed<-101
#source("mtime.R") #A function needed for caching
```

@@

Asymmetry results were generally verified by nonparametric approaches,
with the exception of the methane-flux data. 
For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\cor_l-\cor_u$ were 
(`r unname(round(stat_aphid_ff$numericdf[10,c(3,4)],3))`)
<!--***DAN: Shyamolina, these do not match with the value in table 6! Please check BOTH values and make them correct, and make them agree! You seemed to have used the values for the P statistic by mistake.-->
for the leaf-curling plum aphid first flight data
(Table \ref{tab_multivar_summary}, row 9), 
indicating greater upper-tail dependence, and consistent with
the results of Table \ref{tab_multivar_summary}, row 8. 
For the *Ceratium furca* abundance data, confidence intervals were
(`r unname(round(stat_plankton_north_sea$numericdf[10,c(3,4)],3))`),
<!--***DAN: Shyamolina, these do not match with the value in table 6! Please check BOTH values and make them correct, and make them agree! You seemed to have used the values for the P statistic by mistake.-->
indicating greater lower-tail dependence, and again 
consistent with the results of Table \ref{tab_multivar_summary} (row 9).
For the methane-flux data, confidence intervals were 
(`r unname(round(stat_methane$numericdf[10,c(3,4)],3))`);
<!--***DAN: Shyamolina, these do not match with the value in table 6! Please check BOTH values and make them correct, and make them agree! You seemed to have used the values for the P statistic by mistake.-->
the asymmetry in tail dependence revealed by the model selection
results for the methane-flux data was apparently not strong enough to
also be revealed by the nonparametric analyses. 
Analogues to Table \ref{tab_count_resamp} are in Tables
\ref{SM-tab_ff_resamp}-\ref{SM-tab_methane_resamp}.
Our generally
affirmative, empirically based answer to Q1 for the multivariate datasets is 
represented in Fig. \ref{MasterFigure} as solid outlines around the names
of those datasets, in the middle row of boxes.
We also carried out the same analyses for abundance and first-flight data for the 18 
aphid species for which we had data other than the green spruce and leaf-curling plum aphids,
as well as for the 21 plankton taxa for which we had abundance data other than
\textit{Ceratium furca} (results not shown); results supported the conclusion that 
non-normal copula structure and tail dependence, and asymmetry of tail associations, are 
common.

@@

row.names(tab_multivar_summary_ed)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(
            Description = c("1. Location pairs (excluding self comparisons)",
           "2. Number of non-independent pairs",
           "3. Number of pairs with non-normal copula as best fit",
           "4. Average of AIC differences (normal AIC minus min AIC) across location pairs",
           "5. Number of well-fitting location pairs",
           "6. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. lower-tail dependence",
           "7. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. upper-tail dependence",
           "8. Percent pairs showing stronger lower tail dependence",
           "9. Mean with 2.5$^{th}$ and 97.5$^{th}$ quantiles of Cor$_{l}$ - Cor${_u}$ across all location pair")
           )

>>>>

```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
options(scipen = 1, digits = 3) #This option round all numbers appeared in the inline r code upto specified digit
#seed<-101
#source("mtime.R") #A function needed for caching
```

@@

Asymmetry results were generally verified by nonparametric approaches,
with the exception of the methane-flux data. 
For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\cor_l-\cor_u$ were 
(`r unname(round(stat_aphid_ff$numericdf[9,c(3,4)],3))`)
for the leaf-curling plum aphid first flight data
(Table \ref{tab_multivar_summary}, row 9), 
indicating greater upper-tail dependence, and consistent with
the results of Table \ref{tab_multivar_summary}, row 8. 
For the *Ceratium furca* abundance data, confidence intervals were
(`r unname(round(stat_plankton_north_sea$numericdf[9,c(3,4)],3))`),
indicating greater lower-tail dependence, and again 
consistent with the results of Table \ref{tab_multivar_summary} (row 9).
For the methane-flux data, confidence intervals were 
(`r unname(round(stat_methane$numericdf[9,c(3,4)],3))`);
the asymmetry in tail dependence revealed by the model selection
results for the methane-flux data was apparently not strong enough to
also be revealed by the nonparametric analyses. 
Analogues to Table \ref{tab_count_resamp} are in Tables
\ref{SM-tab_ff_resamp}-\ref{SM-tab_methane_resamp}.
Our generally
affirmative, empirically based answer to Q1 for the multivariate datasets is 
represented in Fig. \ref{MasterFigure} as solid outlines around the names
of those datasets, in the middle row of boxes.
We also carried out the same analyses for abundance and first-flight data for the 18 
aphid species for which we had data other than the green spruce and leaf-curling plum aphids,
as well as for the 21 plankton taxa for which we had abundance data other than
\textit{Ceratium furca} (results not shown); results supported the conclusion that 
non-normal copula structure and tail dependence, and asymmetry of tail associations, are 
common.

@@

row.names(tab_multivar_summary_ed)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(
            Description = c("1. Location pairs (excluding self comparisons)",
           "2. Number of non-independent pairs",
           "3. Number of pairs with non-normal copula as best fit",
           "4. Average of AIC differences (normal AIC minus min AIC) across location pairs",
           "5. Number of well-fitting location pairs",
           "6. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. lower-tail dependence",
           "7. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. upper-tail dependence",
           "8. Percent pairs showing stronger lower tail dependence",
           "9. Mean with 2.5$^{th}$ and 97.5$^{th}$ quantiles of cor$_{l}$ - cor${_u}$ across all location pair")
           )
